Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-09 ms.tex
updated abstract2

\begin{abstract}
Steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies are calculated for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.  Neglecting radiative cooling, analytic estimates are derived for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.  We assess over what range of conditions radiative instability will develop, assuming a star formation history corresponding to the average of that for galaxies of a given black hole mass.  Our main conclusion is that.....  Implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies, are briefly discussed.
\end{abstract}

>>>>

\begin{abstract}
Steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies are calculated for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.  Analytic estimates are derived, neglecting radiative cooling, for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.  These results are used to assess over what range of conditions radiative instability will develop, assuming a feedback due to the average star formation history for galaxies of the given black hole mass.  Our main conclusion is that.....  Implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies, are briefly discussed.
\end{abstract}
